\textsc{Atomic modeling of argon}\\ \footnotesize{\textsc{Project 5 --- FYS3150}}

### 2015-12-07 projects/project_5/molecular_dynamics/article/article.tex
cleaning up

\documentclass[a4paper]{article}
\usepackage[]{enumerate} 
\usepackage[]{graphicx} 
\usepackage[]{subcaption} 
\usepackage[]{amsthm, amsmath, amssymb} 
\usepackage[]{fancyhdr}
\usepackage[]{setspace} 
\usepackage[]{hyperref} 
\urlstyle{sf}
\graphicspath{{../pictures/}}

\renewcommand{\vec}[1]{\mathbf{#1}}

@@

\begin{abstract}
    In this project we explore the world of molecular dynamics. We are first
    presented with the skeleton of a working MD-program, and we are asked to
    implement the functionality we need as we go along. We look at the time
    evolution of a system of argon, with an initial face-centered cubic lattice
    configuration. The atoms are under the influence of the Lennard-Jones
    potential. We use the Velocity-Verlet as our time integrator of choice, and
    we compare this to the Euler-Cromer method in terms of energy conservation
    properties. We also compute the melting temperature of argon, by means of
    the Einstein relation and diffusion constant.
\end{abstract}
\clearpage
\doublespacing
\tableofcontents
\listoffigures      
\singlespacing
\clearpage
\section{Introduction}
\label{sec:introduction}

@@

    We need to chose the parameters $\sigma$ and $\varepsilon$ so that they are
    suited for simulation of argon. It turns out that $\sigma = 3.405
    \mathrm{\AA}$ and $\varepsilon = 119.8k_B\mathrm{K}$ with $k_B = 1$ in
    MD-units.

@@

We also considered the melting temperature of argon, and measured it to be
somewhere close to $300K$, which does not really coincide with the
experimentally observed melting temperature of approximately $84K$. Despite
this disparity the system at least behaves consistent.

>>>>

\documentclass[a4paper]{article}
\usepackage[]{enumerate} 
\usepackage[]{graphicx} 
\usepackage[]{xcolor} 
\usepackage[]{subcaption} 
\usepackage[]{amsthm, amsmath, amssymb} 
\usepackage[]{fancyhdr}
\usepackage[]{setspace} 
\usepackage[]{hyperref} 
\urlstyle{sf}
\graphicspath{{../pictures/}}

\renewcommand{\vec}[1]{\mathbf{#1}}
\newcommand*{\github}[1]{\def\@github{\color{gray!70}#1}}
\newcommand{\githublogo}{\raisebox{-1pt}{\includegraphics[height=9pt]{github}}}

@@

\begin{abstract}
    In this project we explore the world of molecular dynamics. We are first
    presented with the skeleton of a working MD-program, and we are asked to
    implement the functionality we need as we go along. We look at the time
    evolution of a system of argon, with an initial face-centered cubic lattice
    configuration. The atoms are under the influence of the Lennard-Jones
    potential. We use the Velocity-Verlet as our time integrator of choice, and
    we compare this to the Euler-Cromer method in terms of energy conservation
    properties. We also compute the melting temperature of argon, by means of
    the Einstein relation and diffusion constant. All visualizations of the
    system has been performed using the program \texttt{VMD}.\\
    \noindent
    As always, relevant code can be found on my GitHub page:\\

    \centering{\href{https://github.com/qTipTip/FYS3150}{\githublogo \,
    \color{gray!50}\textit{github.com/qTipTip}}}
\end{abstract}
\clearpage
\doublespacing
\tableofcontents
\listoffigures      
\singlespacing
\clearpage
\section{Introduction}
\label{sec:introduction}

@@

    We need to chose the parameters $\sigma$ and $\varepsilon$ so that they are
    suited for simulation of argon. It turns out that $\sigma = 3.405
    \mathrm{\AA}$ and $\varepsilon = 119.8k_B\mathrm{K}$ with $k_B = 1$ in
    MD-units are appropriate values for argon.

@@

We also considered the melting temperature of argon, and measured it to be
somewhere close to $300K$, which does not really coincide with the
experimentally observed melting temperature of approximately $84K$. Despite
this disparity the system at least behaves consistently.
